---
title: "Ethan_Hylton_Indy_Star"
output: html_document
date: "2025-04-22"
---



Draft Pitch:

Ethan Hylton
301-219-4246 / Ethanjhylton@gmail.com
6/2/2025

Hello Mr. Herzong & Wells,

I’d like to pitch a story that looks beyond the betting slips to explore how online sports betting has rapidly overtaken Indiana’s gambling market — and who’s profiting behind the scenes.

Since mobile sports betting launched in Indiana in October 2019, the industry has exploded. While retail sportsbooks exist, they’ve been steadily eclipsed by online platforms, which now account for the vast majority of sports wagers in the state. The public-facing apps like FanDuel, DraftKings, BetMGM, and others are just one layer. What’s less understood is the network of companies, partnerships, and in-state casinos enabling this surge.

Each mobile sportsbook in Indiana must partner with a local brick-and-mortar casino. That’s opened the door for a mix of major national brands and global players to take hold of the market:

FanDuel (owned by Flutter Entertainment, based in Dublin) is partnered with Belterra Casino.

DraftKings (publicly traded in the U.S.) works with Ameristar Casino in East Chicago.

BetMGM is backed by MGM Resorts and UK-based Entain, partnered with Belterra.

Caesars Online operates under the Caesars Entertainment umbrella, tied to its physical casino holdings.

BetRivers is run by Rush Street Interactive, a Chicago-based company, via French Lick Casino.

PointsBet (recently acquired by Fanatics) partnered with Hollywood Casino.

Unibet, from Sweden’s Kindred Group, is paired with Horseshoe Hammond.

BetAmerica (owned by Churchill Downs) has been rebranded or absorbed into TwinSpires.

Betway, owned by Super Group (a global brand based in Malta), is also active in Indiana.
	

This story would explore:
The growth and dominance of online betting over retail locations, using state revenue data


How Google search interest in sports betting has sustained high levels since 2019
The little-known partnerships between global corporations and local Indiana casinos


Whether Indiana is becoming a model — or cautionary tale — for other states following suit


I believe there’s real value in tracing both the cultural shift and the business web that powers Indiana’s mobile betting boom.

<iframe src='https://flo.uri.sh/visualisation/23600704/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23600704/?utm_source=embed&utm_campaign=visualisation/23600704' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>

Part 2:

Hello Mr. Herzong & Wells,

I’ve embedded an interactive Flourish chart comparing monthly revenue growth between retail and online sports betting in Indiana since legalization. What stands out immediately is how aggressively online betting has surged past retail, the gap widens dramatically starting in 2020, reinforcing the market dominance of digital platforms over time. You can visually trace how retail receipts plateau while online gross receipts skyrocket, especially after the COVID-era acceleration.

<iframe src='https://flo.uri.sh/visualisation/23636754/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23636754/?utm_source=embed&utm_campaign=visualisation/23636754' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>


That said, to make room for more historical context and potentially expand the dataset going back further, I may revise the chart to display quarterly totals instead of monthly. It’ll reduce visual clutter while still preserving the broader trend narrative.
I’m also developing a second chart that’ll break down which online sportsbooks have performed best over time. This brand-level data should help us illustrate not just the dominance of the digital sector, but which companies are winning the market share battle month-over-month. I think that insight will pair nicely with the current visual and strengthen our overall argument. This won’t take long for me to develop. 

Beyond the charts, I plan to do more digging into Indiana’s political landscape around gambling. What caught my attention is that many of the state’s “brick-and-mortar” casinos appear to have formal partnerships with online sportsbooks, something that doesn’t seem to be common nationwide. I need to confirm this through further research, but it could speak to a unique regulatory framework or business strategy that’s worth highlighting in the piece.



















# Load software libraries
```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)
library(lubridate)
library(rvest)


```


# Load your data

2024


```{r}

# 
# YOUR_DATA <- read.csv("../data/XXXXX.csv") |> 
#     clean_names()

# 1: Load Excel files (2019–2025)







```

Data details:


# Explore the data types
```{r}

#glimpse(YOUR_DATA)

#glimpse(data_2024)

```
# Fix dates
```{r}
#data_2024 <- data_2024 |> 
  #mutate(date_month = "Dec_2024")


```



# Import data for 2023, 2023
/data/2023-12-Revenue.xlsx
/data/2022-12-Revenue.xlsx





    clean_names()
    

# Questions 

Write down questions you want answered:



# Data Details
Monthly report in PDF form
https://www.in.gov/igc/files/2025-03-Revenue.pdf



Check this annual report for context: https://www.in.gov/igc/files/FY2024-Annual.pdf

Revenue reports:
https://www.in.gov/igc/publications/archived-monthly-revenue-reports/
