---
title: "Ethan_Hylton_Indy_Star"
output: html_document
date: "2025-04-22"
---

A demo notebook for Dow Jones News Fund data interns

During the week’s training, you will work on a project called Investigate Your Community to produce detailed story pitches relevant to their summer internship positions. The goal is to have the students research a topic relevant to your newsroom so they can get to work immediately at the internship. 

Here are some examples from last year’s DJNF data journalism training:

Hannah Rosenberger, at ASI Media/Counselor magazine, produced this analysis on name, image and likeness trends: https://hrosenberger.github.io/ASI-NIL-Project/

Shifra Dayak, an intern at the Connecticut Mirror, produced this analysis of environment spill data: https://shifradayak.github.io/DJNF_Merrill/ct_env_spills.html.

Michael Zhang, an intern at the Houston Landing, explored local election data: https://michaelzhangreporter.github.io/Houston_Campaign_Finance/


Here's what your newsroom suggested for a project
I would like Ethan to look at Indiana gambling revenue for 2015-2024. The data is available in Excel format here https://www.in.gov/igc/publications/archived-monthly-revenue-reports/ the site also has YTD for 2025


I'm not sure what exactly we are looking for, but would like to be able to track total amount of money flowing through casinos -- including revenue trends for individual casinos -- and online sports betting sites; how much goes to the state and "winners"; and look at the growth and impact of online sports betting that became legal in October 2019. 


I am especially interested in the online sports betting because it is relatively new and doesn't require visiting casinos (which I believe also take sports bets). That would include an over-time look at the amount of money spent by Indiana online bettors and the increasing number of online options available. 


Hopefully, an examination of the data will reveal other story paths.


I'm happy to talk if you have questions or thoughts.


Thanks again.
Tim



This notebook helps you get started

# Load software libraries
```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)

```


# Load your data

2024

```{r}

# 
# YOUR_DATA <- read.csv("../data/XXXXX.csv") |> 
#     clean_names()

data_2024 <- read_excel("../data/2024-12-Revenue.xlsx", skip=2) |> 
    clean_names()


```

Data details:


# Explore the data types
```{r}

#glimpse(YOUR_DATA)

glimpse(data)

```
# Fix dates
```{r}
data_2024 <- data_2024 |> 
  mutate(date_month = "Dec_2024")
```



# Import data for 2023, 2023
/data/2023-12-Revenue.xlsx
/data/2022-12-Revenue.xlsx

```{r}

```




# Questions 

Write down questions you want answered:



# Data Details
Monthly report in PDF form
https://www.in.gov/igc/files/2025-03-Revenue.pdf



Check this annual report for context: https://www.in.gov/igc/files/FY2024-Annual.pdf

Revenue reports:
https://www.in.gov/igc/publications/archived-monthly-revenue-reports/
