---
title: "Indiana Sports Betting: Who Are the Real Winners?"
output: html_document
date: "2025-06-07"
editor_options: 
  markdown: 
    wrap: 72
---
Since Indiana legalized sports betting in September 2019, the state has seen a massive shift in how Hoosiers place their bets. While former Governor Eric Holcomb promised that legalization would spur economic growth, create jobs, and benefit Indiana-based casinos, the reality playing out in the numbers tells a different story. Online sports betting outlets like DraftKings, FanDuel, and BetMGM have outpaced traditional retail casinos in revenue month after month, raising important questions about who truly benefits from this new gambling landscape. 
This project analyzes those numbers and examines the opaque ecosystem of online operators profiting off Indiana’s laws.

<iframe src='https://flo.uri.sh/visualisation/23600704/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23600704/?utm_source=embed&utm_campaign=visualisation/23600704' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>

“By modernizing our laws, this legislation will spur positive economic growth for our state and for an industry that employs over 11,000 Hoosiers,” Governor Holcomb said in 2019. Unfortunately, a look at the data suggests most of that growth may be happening outside state lines. 
Sports betting isn’t new, but the way it’s done in Indiana is evolving rapidly. As legislative discussions around gambling regulation resurface and other states look to emulate Indiana’s sports betting infrastructure, now is the time to scrutinize the foundations of Indiana’s model. With 2025 state budget conversations approaching, it’s timely to ask whether this system is truly serving Indiana’s economic and civic goals.

<iframe src='https://flo.uri.sh/visualisation/23636754/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23636754/?utm_source=embed&utm_campaign=visualisation/23636754' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>

Who Cares?:
This story matters to every Indiana taxpayer, policymaker, and sports bettor. Tax revenues and consumer protections hinge on how this system is managed. If out-of-state corporations are capturing the majority of revenue while Indiana sees limited reinvestment, that has major implications for economic justice and public policy. For local journalism and civic accountability, the risk is clear: without scrutiny, Indiana’s model may become a precedent for unchecked corporate gain in the sports betting industry.

Failing to report on this story allows the state’s sports betting system to continue unchecked, potentially replicating a flawed structure in other emerging markets. It prevents voters and lawmakers from making informed decisions on future legislation, and continues to hide the link between power and profit from the public. 

Target Audience:
This story targets Indiana residents, especially sports bettors, legislators, regulators, and a broader national audience following gambling trends, digital markets, and regulatory policy.

Data Analysis Process:

This project began with downloading and cleaning hundreds of rows of monthly revenue data from the Indiana Gaming Commission’s public reports, a process made unnecessarily difficult by inconsistent formatting and file types. After creating a functional dataset using Google Sheets and RStudio, I produced visualizations to compare the performance of retail versus online sports betting operations. I also investigated the companies behind Indiana’s top platforms, uncovering how out-of-state brands partner with in-state casinos to gain legal access while keeping the bulk of profits.

FanDuel, an Irish-American multinational sports betting and gambling company. (owned by Flutter Entertainment, based in Dublin) is partnered with Belterra Casino. 
DraftKings (publicly traded in the U.S.) works with Ameristar Casino in East Chicago. 
BetMGM is backed by MGM Resorts and UK-based Entain, partnered with Belterra.


Next Steps:
Continue analyzing revenue data through YTD 2025.


Compare tax revenue collected by the state to profits collected by online operators.


Dig into the ethics investigation surrounding Spectacle Entertainment and former Governor Holcomb’s connections to casino-linked firms.


Interview economic analysts and casino workers to evaluate whether job creation and local impact promises have held up.


Conclusion:
As Indiana becomes a model for sports betting expansion, it’s critical to scrutinize the structure and outcomes of its legislation. Are we watching the democratization of gambling access, or the quiet consolidation of profit by digital middlemen? This story doesn’t just follow the money, it asks who’s winning, and at what cost.


# Load software libraries

```{r}
#install.packages("tidyverse")
#install.packages("janitor")
#install.packages("readxl")
#install.packages("rvest")
library(tidyverse)
library(janitor)
library(readxl)
library(rvest)
library(lubridate)
library(rvest)


```

<iframe src='https://flo.uri.sh/visualisation/23600704/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23600704/?utm_source=embed&utm_campaign=visualisation/23600704' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>

Part 2:

Hello Mr. Herzong & Wells,

I’ve embedded an interactive Flourish chart comparing monthly revenue growth between retail and online sports betting in Indiana since legalization. What stands out immediately is how aggressively online betting has surged past retail, the gap widens dramatically starting in 2020, reinforcing the market dominance of digital platforms over time. You can visually trace how retail receipts plateau while online gross receipts skyrocket, especially after the COVID-era acceleration.

<iframe src='https://flo.uri.sh/visualisation/23636754/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe><div style='width:100%!;margin-top:4px!important;text-align:right!important;'><a class='flourish-credit' href='https://public.flourish.studio/visualisation/23636754/?utm_source=embed&utm_campaign=visualisation/23636754' target='_top' style='text-decoration:none!important'><img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a></div>


That said, to make room for more historical context and potentially expand the dataset going back further, I may revise the chart to display quarterly totals instead of monthly. It’ll reduce visual clutter while still preserving the broader trend narrative.
I’m also developing a second chart that’ll break down which online sportsbooks have performed best over time. This brand-level data should help us illustrate not just the dominance of the digital sector, but which companies are winning the market share battle month-over-month. I think that insight will pair nicely with the current visual and strengthen our overall argument. This won’t take long for me to develop. 

Beyond the charts, I plan to do more digging into Indiana’s political landscape around gambling. What caught my attention is that many of the state’s “brick-and-mortar” casinos appear to have formal partnerships with online sportsbooks, something that doesn’t seem to be common nationwide. I need to confirm this through further research, but it could speak to a unique regulatory framework or business strategy that’s worth highlighting in the piece.






<pre> ```{=html} <iframe src='https://flo.uri.sh/visualisation/23600704/embed' title='Interactive or visual content' class='flourish-embed-iframe' frameborder='0' scrolling='no' style='width:100%;height:600px;' sandbox='allow-same-origin allow-forms allow-scripts allow-downloads allow-popups allow-popups-to-escape-sandbox allow-top-navigation-by-user-activation'></iframe> <div style='width:100%!;margin-top:4px!important;text-align:right!important;'> <a class='flourish-credit' href='https://public.flourish.studio/visualisation/23600704/?utm_source=embed&utm_campaign=visualisation/23600704' target='_top' style='text-decoration:none!important'> <img alt='Made with Flourish' src='https://public.flourish.studio/resources/made_with_flourish.svg' style='width:105px!important;height:16px!important;border:none!important;margin:0!important;'> </a> </div> ``` </pre>


Part 2:

Hello Mr. Herzong & Wells,

I’ve embedded an interactive Flourish chart comparing monthly revenue growth between retail and online sports betting in Indiana since legalization. What stands out immediately is how aggressively online betting has surged past retail, the gap widens dramatically starting in 2020, reinforcing the market dominance of digital platforms over time. You can visually trace how retail receipts plateau while online gross receipts skyrocket, especially after the COVID-era acceleration.

That said, to make room for more historical context and potentially expand the dataset going back further, I may revise the chart to display quarterly totals instead of monthly. It’ll reduce visual clutter while still preserving the broader trend narrative.
I’m also developing a second chart that’ll break down which online sportsbooks have performed best over time. This brand-level data should help us illustrate not just the dominance of the digital sector, but which companies are winning the market share battle month-over-month. I think that insight will pair nicely with the current visual and strengthen our overall argument. This won’t take long for me to develop. 

Beyond the charts, I plan to do more digging into Indiana’s political landscape around gambling. What caught my attention is that many of the state’s “brick-and-mortar” casinos appear to have formal partnerships with online sportsbooks, something that doesn’t seem to be common nationwide. I need to confirm this through further research, but it could speak to a unique regulatory framework or business strategy that’s worth highlighting in the piece.




Draft Pitch:

Ethan Hylton 301-219-4246 /
[Ethanjhylton\@gmail.com](mailto:Ethanjhylton@gmail.com){.email}
6/2/2025

Hello Mr. Herzong & Wells,

I’d like to pitch a story that looks beyond the betting slips to explore
how online sports betting has rapidly overtaken Indiana’s gambling
market, and who’s profiting behind the scenes.

Since mobile sports betting launched in Indiana in October 2019, the
industry has exploded. While retail sportsbooks exist, they’ve been
steadily eclipsed by online platforms, which now account for the vast
majority of sports wagers in the state. The public-facing apps like
FanDuel, DraftKings, BetMGM, and others are just one layer. What’s less
understood is the network of companies, partnerships, and in-state
casinos enabling this surge.

```{r}

library(tidyverse)




```

Each mobile sportsbook in Indiana must partner with a local
brick-and-mortar casino. That’s opened the door for a mix of major
national brands and global players to take hold of the market: **#rsw
comment: great to figure out this unusual competitive partnership. is
that the case in other states? good progress to nail down these business
partnerships**

-   FanDuel (owned by Flutter Entertainment, based in Dublin) is
    partnered with [Belterra Casino.]{.underline}**#rsw comment
    independent or owned by a British chain?**

-   DraftKings (publicly traded in the U.S.) works with [Ameristar
    Casino in East Chicago]{.underline}.**#rsw comment independent or
    owned by a chain?**

-   BetMGM is backed by MGM Resorts and UK-based Entain, partnered with
    Belterra.

-   Caesars Online operates under the Caesars Entertainment umbrella,
    tied to its physical casino holdings. **#rsw comment: so maybe
    Caesars has the less to lose since it is vertically integrated?**

-   BetRivers is run by Rush Street Interactive, a Chicago-based
    company, via [French Lick Casino.]{.underline}**#rsw comment
    independent or owned by a chain?**

-   PointsBet (recently acquired by Fanatics) partnered with Hollywood
    Casino. **#rsw comment. hollywood is a chain, I'm pretty sure**

-   Unibet, from Sweden’s Kindred Group, is paired with [Horseshoe
    Hammond.]{.underline} **#rsw comment independent or owned by a
    chain?**

-   BetAmerica (owned by Churchill Downs) has been rebranded or absorbed
    into TwinSpires.

-   Betway, owned by Super Group (a global brand based in Malta), is
    also active in Indiana.\
    \
    This story would explore: The growth and dominance of online betting
    over retail locations, using state revenue data

How Google search interest in sports betting has sustained high levels
since 2019. The little-known partnerships between global corporations
and local Indiana casinos

Whether Indiana is becoming a model, or cautionary tale for other
states following suit

I believe there’s real value in tracing both the cultural shift and the
business web that powers Indiana’s mobile betting boom.

# Load your data

2024

```{r}









```



